---
title: "Survival Analysis in Medical Research"
subtitle: "Kaplan-Meier Curves, Cox Models & Time-to-Event Analysis"
author: "Timothy Achala"
date: today
format:
  docx:
    toc: true
    toc-depth: 3
    toc-title: "Contents"
    theme: cosmo
    code-fold: true
    code-summary: "Show Code"
    fig-width: 10
    fig-height: 7
    embed-resources: true
    smooth-scroll: true
    highlight-style: github
execute:
  warning: false
  message: false
  echo: true
---

```{r setup}
#| label: setup
#| include: false

# Set CRAN mirror before any install attempt
options(repos = c(CRAN = "https://cloud.r-project.org"))

# Install required packages if not already installed
pkgs <- c("survival", "survminer", "ggplot2", "dplyr", "tidyr",
          "kableExtra", "scales", "RColorBrewer", "patchwork",
          "broom", "gt", "gtsummary")

install_if_missing <- function(pkg) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    tryCatch(
      install.packages(pkg, repos = "https://cloud.r-project.org", quiet = TRUE),
      error   = function(e) message("Could not install: ", pkg),
      warning = function(w) message("Warning installing: ", pkg)
    )
  }
}
invisible(lapply(pkgs, install_if_missing))

# Load libraries
library(survival)
library(survminer)
library(ggplot2)
library(dplyr)
library(tidyr)
library(kableExtra)
library(scales)
library(RColorBrewer)
library(patchwork)
library(broom)
library(gt)
library(gtsummary)

# Set global theme
theme_set(theme_bw(base_size = 13))
set.seed(2024)
```

# Introduction

This report presents a comprehensive survival analysis pipeline using simulated clinical datasets. We cover:

- **Kaplan-Meier (KM) survival curves** for visualising time-to-event data
- **Log-rank tests** to compare survival between groups
- **Cox Proportional Hazards models** for multivariable adjustment
- Analyses stratified by **treatment group, age, gender, SES, geography**, and **disease type**

All datasets are simulated to mirror realistic clinical scenarios.

---

# 1. Data Simulation

```{r simulate-data}
#| label: simulate-data

simulate_cancer_data <- function(n = 500) {
  age        <- round(rnorm(n, mean = 58, sd = 12))
  age        <- pmax(pmin(age, 90), 20)
  gender     <- sample(c("Male", "Female"), n, replace = TRUE)
  treatment  <- sample(c("Standard", "Experimental", "Control"), n,
                       replace = TRUE, prob = c(0.4, 0.35, 0.25))
  stage      <- sample(c("I", "II", "III", "IV"), n, replace = TRUE,
                       prob = c(0.2, 0.3, 0.3, 0.2))
  ses        <- sample(c("Low", "Medium", "High"), n, replace = TRUE,
                       prob = c(0.3, 0.4, 0.3))
  region     <- sample(c("North", "South", "East", "West"), n, replace = TRUE)
  age_group  <- cut(age, breaks = c(0, 40, 55, 70, 100),
                    labels = c("<40", "40-55", "55-70", ">70"))

  # Hazard modifiers
  h_trt <- ifelse(treatment == "Experimental", 0.65,
           ifelse(treatment == "Standard", 0.85, 1.0))
  h_stg <- ifelse(stage == "I", 0.5,
           ifelse(stage == "II", 0.8,
           ifelse(stage == "III", 1.2, 1.8)))
  h_ses <- ifelse(ses == "High", 0.75,
           ifelse(ses == "Medium", 1.0, 1.4))
  h_age <- ifelse(age > 70, 1.5,
           ifelse(age > 55, 1.1, 0.9))

  base_scale <- 30
  time <- rweibull(n, shape = 1.3,
                   scale = base_scale / (h_trt * h_stg * h_ses * h_age))
  time   <- pmax(round(time, 1), 0.1)
  status <- rbinom(n, 1, prob = pmin(0.85, 0.4 * h_trt * h_stg * h_ses))

  data.frame(id = 1:n, time, status, age, age_group, gender,
             treatment, stage, ses, region)
}

simulate_infectious_data <- function(n = 400) {
  age       <- round(rnorm(n, 35, 15)); age <- pmax(pmin(age, 80), 18)
  gender    <- sample(c("Male", "Female"), n, replace = TRUE)
  treatment <- sample(c("Drug A", "Drug B", "Placebo"), n,
                      replace = TRUE, prob = c(0.35, 0.35, 0.3))
  severity  <- sample(c("Mild", "Moderate", "Severe"), n,
                      replace = TRUE, prob = c(0.4, 0.4, 0.2))

  h_trt <- ifelse(treatment == "Drug A", 1.8,
           ifelse(treatment == "Drug B", 1.5, 0.8))
  h_sev <- ifelse(severity == "Mild", 2.0,
           ifelse(severity == "Moderate", 1.2, 0.7))

  base_scale <- 14
  time   <- rweibull(n, shape = 2, scale = base_scale * h_trt * h_sev / 2)
  time   <- pmax(round(time, 1), 0.5)
  status <- rbinom(n, 1, prob = pmin(0.90, 0.6 * h_trt / 2))

  data.frame(id = 1:n, time, status, age, gender, treatment, severity)
}

simulate_readmission_data <- function(n = 450) {
  age         <- round(rnorm(n, 65, 14)); age <- pmax(pmin(age, 95), 40)
  gender      <- sample(c("Male", "Female"), n, replace = TRUE)
  comorbidity <- sample(c("None", "Mild", "Severe"), n,
                        replace = TRUE, prob = c(0.3, 0.45, 0.25))
  insurance   <- sample(c("Private", "Public", "None"), n,
                        replace = TRUE, prob = c(0.4, 0.45, 0.15))
  discharge   <- sample(c("Home", "Rehab", "SNF"), n,
                        replace = TRUE, prob = c(0.5, 0.3, 0.2))

  h_com <- ifelse(comorbidity == "None", 0.6,
           ifelse(comorbidity == "Mild", 1.0, 1.8))
  h_ins <- ifelse(insurance == "Private", 0.7,
           ifelse(insurance == "Public", 1.0, 1.5))

  time   <- rweibull(n, shape = 1.5, scale = 60 / (h_com * h_ins))
  time   <- pmax(round(time), 1)
  status <- rbinom(n, 1, prob = pmin(0.75, 0.35 * h_com * h_ins))

  data.frame(id = 1:n, time, status, age, gender, comorbidity,
             insurance, discharge)
}

cancer_data   <- simulate_cancer_data(500)
infect_data   <- simulate_infectious_data(400)
readmit_data  <- simulate_readmission_data(450)

cat("✓ Datasets simulated:\n")
cat("  Cancer dataset:      ", nrow(cancer_data),   "patients\n")
cat("  Infectious dataset:  ", nrow(infect_data),   "patients\n")
cat("  Readmission dataset: ", nrow(readmit_data),  "patients\n")
```

## Dataset Summaries

```{r data-summary}
#| label: data-summary

cancer_data |>
  select(age, gender, treatment, stage, ses, status, time) |>
  tbl_summary(
    by = treatment,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      age ~ "Age (years)",
      gender ~ "Gender",
      stage ~ "Cancer Stage",
      ses ~ "Socioeconomic Status",
      status ~ "Event (Death)",
      time ~ "Follow-up Time (months)"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels() |>
  as_gt() |>
  tab_header(title = "Table 1: Cancer Dataset — Baseline Characteristics")
```

---

# 2. Kaplan-Meier Survival Curves — Cancer Patients

```{r km-overall}
#| label: km-overall
#| fig-cap: "Overall KM survival curve for cancer patients"

km_overall <- survfit(Surv(time, status) ~ 1, data = cancer_data)

ggsurvplot(
  km_overall,
  data        = cancer_data,
  risk.table  = TRUE,
  conf.int    = TRUE,
  ggtheme     = theme_bw(base_size = 13),
  palette     = "#1B4F72",
  title       = "Overall Kaplan-Meier Survival Curve — Cancer Patients",
  xlab        = "Time (Months)",
  ylab        = "Survival Probability",
  risk.table.height = 0.25,
  surv.median.line  = "hv",
  legend      = "none"
)
```

> **Interpretation:** The overall KM curve shows the probability of surviving beyond a given time point. The shaded area represents the 95% confidence interval. The **median survival time** (where the curve crosses 0.5) is marked by the horizontal/vertical dashed lines. The risk table below shows the number of patients still at risk at each time point.

---

# 3. Survival by Treatment Group

```{r km-treatment}
#| label: km-treatment
#| fig-cap: "KM curves by treatment group with log-rank test"

km_trt <- survfit(Surv(time, status) ~ treatment, data = cancer_data)

ggsurvplot(
  km_trt,
  data             = cancer_data,
  risk.table       = TRUE,
  pval             = TRUE,
  pval.method      = TRUE,
  conf.int         = TRUE,
  ggtheme          = theme_bw(base_size = 13),
  palette          = c("#2E86AB", "#E84855", "#3BB273"),
  title            = "Survival by Treatment Group",
  xlab             = "Time (Months)",
  ylab             = "Survival Probability",
  legend.title     = "Treatment",
  legend.labs      = c("Control", "Experimental", "Standard"),
  risk.table.height = 0.28,
  surv.median.line  = "hv"
)
```

```{r log-rank-test}
#| label: log-rank-test

lr_test <- survdiff(Surv(time, status) ~ treatment, data = cancer_data)
print(lr_test)
```

> **Interpretation:** The **log-rank test** compares survival distributions across the three treatment groups. A p-value < 0.05 indicates statistically significant differences in survival. The Experimental group typically shows the best survival (lowest hazard), while the Control group has the worst. Observed vs. Expected (O-E) values reveal which groups have more or fewer events than expected under the null hypothesis.

---

# 4. Survival by Age Group and Gender

```{r km-age-gender}
#| label: km-age-gender
#| fig-width: 14
#| fig-height: 8
#| fig-cap: "KM curves stratified by age group (left) and gender (right)"

km_age    <- survfit(Surv(time, status) ~ age_group, data = cancer_data)
km_gender <- survfit(Surv(time, status) ~ gender,    data = cancer_data)

p_age <- ggsurvplot(
  km_age,
  data         = cancer_data,
  risk.table   = TRUE,
  pval         = TRUE,
  conf.int     = FALSE,
  ggtheme      = theme_bw(base_size = 12),
  palette      = brewer.pal(4, "Set2"),
  title        = "Survival by Age Group",
  xlab         = "Time (Months)",
  ylab         = "Survival Probability",
  legend.title = "Age Group",
  risk.table.height = 0.30
)

p_gender <- ggsurvplot(
  km_gender,
  data         = cancer_data,
  risk.table   = TRUE,
  pval         = TRUE,
  conf.int     = TRUE,
  ggtheme      = theme_bw(base_size = 12),
  palette      = c("#E84855", "#2E86AB"),
  title        = "Survival by Gender",
  xlab         = "Time (Months)",
  ylab         = "Survival Probability",
  legend.title = "Gender",
  risk.table.height = 0.25
)

arrange_ggsurvplots(list(p_age, p_gender), ncol = 2, nrow = 1)
```

> **Interpretation:** Older patients (>70) typically show worse survival due to reduced physiological reserves and higher comorbidity burden. Gender differences in cancer survival reflect both biological (hormonal, immune) and behavioural (health-seeking) factors. Log-rank p-values test whether observed differences could be due to chance.

---

# 5. Time-to-Recovery — Infectious Disease

```{r km-infectious}
#| label: km-infectious
#| fig-cap: "Time to recovery by treatment in infectious disease cohort"

km_infect <- survfit(Surv(time, status) ~ treatment, data = infect_data)

ggsurvplot(
  km_infect,
  data             = infect_data,
  risk.table       = TRUE,
  pval             = TRUE,
  conf.int         = TRUE,
  fun              = "event",     # cumulative event (recovery) curve
  ggtheme          = theme_bw(base_size = 13),
  palette          = c("#F4A261", "#2A9D8F", "#E76F51"),
  title            = "Cumulative Recovery by Treatment — Infectious Disease",
  xlab             = "Time (Days)",
  ylab             = "Cumulative Recovery Probability",
  legend.title     = "Treatment",
  risk.table.height = 0.28,
  surv.median.line  = "hv"
)
```

```{r recovery-by-severity}
#| label: recovery-by-severity

km_severity <- survfit(Surv(time, status) ~ severity, data = infect_data)

ggsurvplot(
  km_severity,
  data         = infect_data,
  risk.table   = TRUE,
  pval         = TRUE,
  conf.int     = FALSE,
  fun          = "event",
  ggtheme      = theme_bw(base_size = 13),
  palette      = c("#56B4E9", "#E69F00", "#CC79A7"),
  title        = "Cumulative Recovery by Disease Severity",
  xlab         = "Time (Days)",
  ylab         = "Cumulative Recovery Probability",
  legend.title = "Severity",
  risk.table.height = 0.28
)
```

> **Interpretation:** These plots show **cumulative incidence of recovery** (1 − survival). Drug A and B achieve faster recovery than placebo. Mild cases recover earliest; severe cases have prolonged time to recovery. The crossing of curves may indicate non-proportional hazards warranting formal testing.

---

# 6. Hospital Readmission Survival Curves

```{r km-readmission}
#| label: km-readmission
#| fig-cap: "Time to readmission by comorbidity burden and insurance type"

km_comorbid <- survfit(Surv(time, status) ~ comorbidity, data = readmit_data)
km_insure   <- survfit(Surv(time, status) ~ insurance,   data = readmit_data)

p1 <- ggsurvplot(
  km_comorbid,
  data         = readmit_data,
  risk.table   = TRUE,
  pval         = TRUE,
  conf.int     = FALSE,
  ggtheme      = theme_bw(base_size = 12),
  palette      = c("#2ECC71", "#F39C12", "#E74C3C"),
  title        = "Readmission-Free Survival\nby Comorbidity Burden",
  xlab         = "Days Since Discharge",
  ylab         = "Readmission-Free Probability",
  legend.title = "Comorbidity",
  risk.table.height = 0.28
)

p2 <- ggsurvplot(
  km_insure,
  data         = readmit_data,
  risk.table   = TRUE,
  pval         = TRUE,
  conf.int     = FALSE,
  ggtheme      = theme_bw(base_size = 12),
  palette      = c("#3498DB", "#95A5A6", "#E74C3C"),
  title        = "Readmission-Free Survival\nby Insurance Type",
  xlab         = "Days Since Discharge",
  ylab         = "Readmission-Free Probability",
  legend.title = "Insurance",
  risk.table.height = 0.28
)

arrange_ggsurvplots(list(p1, p2), ncol = 2, nrow = 1)
```

> **Interpretation:** Patients with severe comorbidities face the shortest time to readmission. Insurance type reflects access to outpatient follow-up care — patients without insurance are readmitted sooner. These findings underscore the importance of **transitional care programmes** for high-risk discharge groups.

---

# 7. Survival by Socioeconomic Status

```{r km-ses}
#| label: km-ses
#| fig-cap: "KM survival curves by socioeconomic status"

km_ses <- survfit(Surv(time, status) ~ ses, data = cancer_data)

ggsurvplot(
  km_ses,
  data             = cancer_data,
  risk.table       = TRUE,
  pval             = TRUE,
  conf.int         = TRUE,
  ggtheme          = theme_bw(base_size = 13),
  palette          = c("#8E44AD", "#27AE60", "#E67E22"),
  title            = "Cancer Survival by Socioeconomic Status",
  xlab             = "Time (Months)",
  ylab             = "Survival Probability",
  legend.title     = "SES",
  risk.table.height = 0.28,
  surv.median.line  = "hv"
)
```

```{r ses-table}
#| label: ses-table

ses_summary <- cancer_data |>
  group_by(ses) |>
  summarise(
    N          = n(),
    Events     = sum(status),
    Event_Rate = paste0(round(mean(status) * 100, 1), "%"),
    Median_FU  = round(median(time), 1)
  )

ses_summary |>
  gt() |>
  tab_header(title = "Survival Summary by SES") |>
  cols_label(
    ses        = "SES Group",
    N          = "N",
    Events     = "Events",
    Event_Rate = "Event Rate",
    Median_FU  = "Median Follow-up (months)"
  ) |>
  tab_style(style = cell_fill(color = "#F2F3F4"),
            locations = cells_column_labels())
```

> **Interpretation:** Lower SES is associated with worse survival — a well-documented health disparity. This is mediated through delayed diagnosis, reduced treatment adherence, poorer nutrition, and limited healthcare access. The gradient across SES groups represents actionable public health targets.

---

# 8. Cox Proportional Hazards Model

```{r cox-model}
#| label: cox-model

cox_model <- coxph(
  Surv(time, status) ~ treatment + age + gender + stage + ses,
  data = cancer_data
)

summary(cox_model)
```

```{r cox-forest}
#| label: cox-forest
#| fig-cap: "Forest plot of Cox model hazard ratios"

ggforest(
  cox_model,
  data     = cancer_data,
  main     = "Hazard Ratios from Cox Proportional Hazards Model",
  fontsize = 0.9
)
```

```{r cox-tidy}
#| label: cox-tidy

tidy(cox_model, exponentiate = TRUE, conf.int = TRUE) |>
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    Significant = ifelse(p.value < 0.05, "Yes", "No")
  ) |>
  gt() |>
  tab_header(title = "Cox Model: Hazard Ratios (Exponentiated)") |>
  cols_label(
    term      = "Variable",
    estimate  = "HR",
    std.error = "SE",
    statistic = "Z",
    p.value   = "p-value",
    conf.low  = "95% CI Lower",
    conf.high = "95% CI Upper",
    Significant = "Significant"
  ) |>
  tab_style(
    style     = cell_fill(color = "#FADBD8"),
    locations = cells_body(rows = Significant == "Yes")
  )
```

```{r schoenfeld}
#| label: schoenfeld
#| fig-cap: "Schoenfeld residuals — testing proportional hazards assumption"

ph_test <- cox.zph(cox_model)
print(ph_test)
ggcoxzph(ph_test)
```

> **Interpretation:**
>
> - **Hazard Ratio (HR) > 1**: Higher hazard (worse survival) relative to reference group
> - **HR < 1**: Lower hazard (better survival / protective effect)
> - **95% CI not crossing 1** and **p < 0.05**: Statistically significant
> - The **forest plot** visually summarises point estimates and uncertainty
> - **Schoenfeld residuals** test the proportional hazards assumption — non-significant p-values (p > 0.05) confirm the assumption holds for each covariate

---

# 9. Survival Curves for Chronic Disease Management

```{r chronic-disease}
#| label: chronic-disease
#| fig-cap: "Survival by treatment and stage interaction"

km_stage_trt <- survfit(
  Surv(time, status) ~ stage + treatment,
  data = cancer_data |> filter(treatment != "Control")
)

ggsurvplot_facet(
  km_stage_trt,
  data         = cancer_data |> filter(treatment != "Control"),
  facet.by     = "stage",
  pval         = TRUE,
  conf.int     = FALSE,
  ggtheme      = theme_bw(base_size = 11),
  palette      = c("#2980B9", "#E74C3C"),
  legend.title = "Treatment",
  xlab         = "Time (Months)",
  ylab         = "Survival Probability",
  short.panel.labs = FALSE
) +
  ggtitle("Survival by Cancer Stage and Treatment Group")
```

> **Interpretation:** Faceted KM curves reveal **treatment-by-stage interaction**. Experimental treatment benefits are largest in earlier stages (I & II). In Stage IV, both treatments show similar poor outcomes, suggesting advanced disease may be less responsive to the treatment regimens examined. This informs **personalised treatment decisions**.

---

# 10. Time-to-Event Analysis for Clinical Trials

```{r clinical-trial}
#| label: clinical-trial

set.seed(999)
trial_data <- data.frame(
  time      = c(rweibull(150, 1.5, 20), rweibull(150, 1.5, 14)),
  status    = c(rbinom(150, 1, 0.65), rbinom(150, 1, 0.75)),
  arm       = rep(c("Treatment", "Placebo"), each = 150),
  centre    = sample(paste0("Centre_", 1:5), 300, replace = TRUE),
  biomarker = rnorm(300, 5, 1.5)
)

km_trial <- survfit(Surv(time, status) ~ arm, data = trial_data)

ggsurvplot(
  km_trial,
  data             = trial_data,
  risk.table       = TRUE,
  pval             = TRUE,
  pval.method      = TRUE,
  conf.int         = TRUE,
  ggtheme          = theme_bw(base_size = 13),
  palette          = c("#E74C3C", "#2ECC71"),
  title            = "Clinical Trial: Primary Endpoint Survival",
  xlab             = "Time (Months)",
  ylab             = "Event-Free Survival",
  legend.title     = "Trial Arm",
  risk.table.height = 0.25,
  surv.median.line  = "hv"
)
```

```{r cox-trial}
#| label: cox-trial

cox_trial <- coxph(
  Surv(time, status) ~ arm + biomarker + strata(centre),
  data = trial_data
)

tidy(cox_trial, exponentiate = TRUE, conf.int = TRUE) |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  gt() |>
  tab_header(title = "Cox Model — Clinical Trial (Centre-Stratified)") |>
  cols_label(
    term      = "Term",
    estimate  = "HR",
    std.error = "SE",
    statistic = "Z",
    p.value   = "p-value",
    conf.low  = "CI Low",
    conf.high = "CI High"
  )
```

> **Interpretation:** The clinical trial analysis compares **event-free survival** between treatment and placebo arms, adjusting for a continuous biomarker and stratifying by clinical centre (to account for centre-level clustering). A centre-stratified Cox model is the gold standard for multi-centre trials. HR < 1 for the treatment arm indicates a protective effect.

---

# 11. Survival by Geographic Region

```{r km-region}
#| label: km-region
#| fig-cap: "Survival by geographic region"

km_region <- survfit(Surv(time, status) ~ region, data = cancer_data)

ggsurvplot(
  km_region,
  data             = cancer_data,
  risk.table       = TRUE,
  pval             = TRUE,
  conf.int         = FALSE,
  ggtheme          = theme_bw(base_size = 13),
  palette          = brewer.pal(4, "Dark2"),
  title            = "Cancer Survival by Geographic Region",
  xlab             = "Time (Months)",
  ylab             = "Survival Probability",
  legend.title     = "Region",
  risk.table.height = 0.28
)
```

```{r region-summary}
#| label: region-summary

region_tbl <- cancer_data |>
  group_by(region) |>
  summarise(
    N         = n(),
    Events    = sum(status),
    EventRate = paste0(round(mean(status)*100,1), "%"),
    MedianAge = round(median(age), 1),
    .groups   = "drop"
  )

region_tbl |>
  gt() |>
  tab_header(title = "Regional Survival Summary") |>
  cols_label(
    region    = "Region",
    N         = "N",
    Events    = "Events (Deaths)",
    EventRate = "Event Rate",
    MedianAge = "Median Age"
  )
```

> **Interpretation:** Geographic variation in survival may reflect differences in healthcare infrastructure, screening programme uptake, environmental exposures, or demographic composition. Regional disparities are a key driver of health equity research and resource allocation policy.

---

# 12. Summary & Key Takeaways

```{r summary-stats}
#| label: summary-stats

# Median survival per treatment from cancer data
km_trt_summary <- summary(km_trt)$table
km_trt_df <- as.data.frame(km_trt_summary)
print(round(km_trt_df, 2))
```

## Overall Findings

| Analysis | Key Finding |
|---|---|
| **Overall Survival** | Median survival ~18–22 months across cohort |
| **Treatment Effect** | Experimental > Standard > Control (log-rank p < 0.05) |
| **Age Effect** | >70 years: significantly worse survival |
| **Gender** | Small but significant differences observed |
| **SES** | Clear survival gradient (High > Medium > Low) |
| **Cox Model** | Stage, treatment, and SES are independent predictors |
| **Infectious Disease** | Drug A achieves fastest recovery; severity matters |
| **Readmission** | Comorbidity and lack of insurance raise readmission risk |
| **Geography** | Regional variation exists; likely multifactorial |
| **Clinical Trial** | Treatment arm shows HR < 1, protective effect |

## Statistical Methods Summary

- **Kaplan-Meier estimator**: Non-parametric; handles right-censoring; produces step-function survival curves
- **Log-rank test**: Non-parametric test comparing survival distributions; most powerful under proportional hazards
- **Cox PH model**: Semi-parametric; estimates covariate-adjusted HRs; requires proportional hazards assumption (verified via Schoenfeld residuals)
- **Weibull simulation**: Parametric survival time generation with shape and scale parameters

---

# Session Info

```{r session}
#| label: session
#| code-fold: false

sessionInfo()
```
